---
title: "Experimental Demonstrations - Tests"
author: "Sotirios Liaskos"
format: 
  html:
    toc: true
    toc-depth: 3
    toc-location: left
editor: visual
---

# Overview

```{r echo = FALSE, warning=FALSE, message=FALSE}
source("library.R")
library("gridExtra")
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = TRUE
)

setVars <- function(outputFolder,experiment,txs) {
  outputRelFolder <<- outputFolder
  blockData <<- read_csv(paste0(outputRelFolder,experiment,"/BlockLog - ",experiment,".csv"))
  eventData <<- read_csv(paste0(outputRelFolder,experiment,"/EventLog - ",experiment,".csv"))
  beliefData <<- read_csv(paste0(outputRelFolder,experiment,"/BeliefLogShort - ",experiment,".csv")) %>% 
  rename(Simulation = SimID, Time = `Time (ms from start)`, Transaction = `Transaction ID`)
  producePaceData(outputRelFolder,experiment)
  txVector <<- txs
  experiment <<- experiment
}
```

# Honest Cases {.tabset}

## Normal State

### Overview

-   **Configuration:** `examples/configs/test/normal/test.normal.properties`
-   **Workload Sampler:** `StandardRandom`
-   **Runs With:** `test-normal.sh`

A simple PoW network consisting of $30$ nodes, $100$ seeds, $1000$ transactions arriving at a $\lambda = 0.025$. The arrival rate is $1$ transaction every $40$ seconds, hence the expected time for the arrival of $1000$ transactions is $11.1$ hours. Analysis focuses on the first few minutes; sample transactions are {5, 6, 7, 8 , 9}.

### Data Load

```{r}

experiment = "test.normal - 2026.01.31 11.44.50"

setVars("../../../../cnsim-bitcoin/examples/results/",
        experiment,
        c(5,6,7,8,9))
```

### Pace Analysis

Block pace is based on the network power and the corresponding difficulty. We specifically have:

-   Difficulty = `r (pow.difficulty = 4.3933890848757156E23)`
-   HashPower (mean) = `r (pow.hashPowerMean = 2.8644667E11)` (per node, so total is $30\times$ in G/sec)
-   HashPower (sd) = `r (pow.hashPowerSD = 2.8644667E10)`

The theoretical pace would be:

-   Mean: `r mean(pace_theoretical(1000, pow.difficulty,pow.hashPowerMean * 30 * 1E9)/60)` minutes

-   Standard deviation: `r sd(pace_theoretical(1000, pow.difficulty,pow.hashPowerMean * 30 * 1E9)/60)` minutes

```{R }
paceInfo(outputRelFolder,experiment)
```

### Belief Graphing

```{R }
test.plain.data = prepareGraphData(beliefData,
                                alignTimes = TRUE,
                                VaR = TRUE,
                                arrivalTimes = getTxArrivalTimes(eventData,txVector))
```

```{R }
getBeliefGraph(test.plain.data, xlim = c("0:00","5:00"),threshold = 0.9)
```

### Finality Analysis

```{R }
res = getFinality(beliefData,
            alignTimes = TRUE, 
            threshold = 0.9,
            arrivalTimes = getTxArrivalTimes(eventData,txVector), 
            horizon = "10:00.000") 
res %>% select(Transaction, successes, trials, p_val = threstest_p_val, point_estimate,ci_low,ci_high)
```

```{R }
ggplot(res, aes(x = Transaction, y = point_estimate)) +
  geom_point(color = "blue") +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.5, color = "lightblue") +
  labs(x = "Transaction", 
       y = "Estimated probability of success",
       title = "Point estimates with 95% CI") +
  theme_minimal()
```

```{R }
getTimeToFinality(test.plain.data, 0.9)
```

### Transaction History

```{R eval = FALSE, echo = FALSE}
getTransactionHistory(eventData,blockData,txVector = c(5), simVector = c(10,10))
```

## Workload with a Conflict

### Overview

-   **Configuration:** `examples/configs/test/conflict/test.conflict.properties`
-   **Workload Sampler:** `examples/configs/test/conflict/test.conflict.csv`
-   **Runs With:** \``test-normal.sh`

We adopt the same configuration as above except for a conflict that we hard-code conflict between transactions 5 and 7. We expect transaction 7 to never reach finality due to it coming second.

### Data Load

```{r}
setVars("../../../../cnsim-bitcoin/examples/results/","test.conflict - 2026.01.31 15.29.26",c(5,6,7,8,9))
```

### Pace Analysis

```{R }
paceInfo(outputRelFolder,experiment)
```

### Belief Graphing

```{R }
test.plain.data = prepareGraphData(beliefData,
                                alignTimes = TRUE,
                                VaR = TRUE,
                                arrivalTimes = getTxArrivalTimes(eventData,txVector))
```

```{R }
grid.arrange(
  getBeliefGraph(test.plain.data, xlim = c("0:00","4:00"),threshold = 0.9, VaR = "exclude"),
  getBeliefGraph(test.plain.data, xlim = c("0:00","4:00"),threshold = 0.9, VaR = "only"), ncol = 1
)
```

### Finality Analysis

```{R }
res = getFinality(beliefData,
            alignTimes = TRUE, 
            threshold = 0.9,
            arrivalTimes = getTxArrivalTimes(eventData,txVector), 
            horizon = "10:00.000") 
res %>% select(Transaction, successes, trials, p_val = threstest_p_val, point_estimate,ci_low,ci_high)
```

```{R }
ggplot(res, aes(x = Transaction, y = point_estimate)) +
  geom_point(color = "blue") +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.5, color = "lightblue") +
  labs(x = "Transaction", 
       y = "Estimated probability of success",
       title = "Point estimates with 95% CI") +
  theme_minimal()
```

```{R }
getTimeToFinality(test.plain.data, 0.9)
```

### Transaction History

```{R eval = FALSE, echo = FALSE}
getTransactionHistory(eventData,blockData,txVector = c(5), simVector = c(10,10))
```

## Setting with restricted block size

### Overview

-   **Configuration:** `examples/configs/test/conflict/test.size.properties`
-   **Workload Sampler:** `examples/configs/test/conflict/test.size.csv`
-   **Runs With:** \``test-size.sh`

We adopt the same configuration but increase the size of transaction (from `5Kb` to `200Kb` and decrease the size of the block (from `1MB` to `500Kb`). The resulting bottleneck would imply that some transactions may have longer finality. For simplicity we remove dependencies.

### Data Load

```{r}
setVars("../../../../cnsim-bitcoin/examples/results/","test.size - 2026.01.31 15.38.14", c(5,6,7,8,9))
```

### Pace Analysis

```{R }
paceInfo(outputRelFolder,experiment)
```

### Belief Graphing

```{R }
graphData = prepareGraphData(beliefData,
                                alignTimes = TRUE,
                                VaR = TRUE,
                                arrivalTimes = getTxArrivalTimes(eventData,txVector))
```

Transaction 9 has low value but not small size.

```{R }
grid.arrange(
  getBeliefGraph(graphData, xlim = c("0:00","30:00"),threshold = 0.9, VaR = "exclude"),
  getBeliefGraph(graphData, xlim = c("0:00","30:00"),threshold = 0.9, VaR = "only"), ncol = 1
)
```

### Finality Analysis

```{R }
res = getFinality(beliefData,
            alignTimes = TRUE, 
            threshold = 0.9,
            arrivalTimes = getTxArrivalTimes(eventData,txVector), 
            horizon = "10:00.000") 
res %>% select(Transaction, successes, trials, p_val = threstest_p_val, point_estimate,ci_low,ci_high)
```

```{R }
ggplot(res, aes(x = Transaction, y = point_estimate)) +
  geom_point(color = "blue") +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.5, color = "lightblue") +
  labs(x = "Transaction", 
       y = "Estimated probability of success",
       title = "Point estimates with 95% CI") +
  theme_minimal()
```

```{R }
getTimeToFinality(test.plain.data, 0.9)
```

### Transaction History

```{R eval = FALSE, echo = FALSE}
getTransactionHistory(eventData,blockData,txVector = c(5), simVector = c(10,10))
```

## Restricted block size and uneven values

### Overview

-   **Configuration:** `examples/configs/test/conflict/test.value.properties`
-   **Workload Sampler:** `examples/configs/test/conflict/test.value.csv`
-   **Runs With:** \``test-value.sh`

### Data Load

```{r}
experiment = "test.value - 2026.01.31 16.03.07"
setVars("../../../../cnsim-bitcoin/examples/results/",experiment, c(5,6,7,8,9,10,11))
```

We adopt the same configuration as above, except that transactions `5-11` (a) keep sizes stable to `200,000` (b) increase sizes from `250` to `3,000`.

```{R}
inp <- read_csv(paste0(outputRelFolder,experiment,"/Input - ",experiment,".csv"))
print(inp %>% filter(TxID %in% txVector, SimID == 1) %>% select(TxID,Size,Value) %>% arrange(TxID))
```

We also allow update of seeds from the beginning of the simulation to allow for more variability, given the closeness of the sample transactions.

### Pace Analysis

```{R }
paceInfo(outputRelFolder,experiment)
```

### Belief Graphing

```{R }
graphData = prepareGraphData(beliefData,
                                alignTimes = TRUE,
                                VaR = TRUE,
                                arrivalTimes = getTxArrivalTimes(eventData,txVector))
```

```{R }
grid.arrange(
  getBeliefGraph(graphData, xlim = c("0:00","20:00"),threshold = 0.9, VaR = "exclude"),
  getBeliefGraph(graphData, xlim = c("0:00","20:00"),threshold = 0.9, VaR = "only"), ncol = 1
)
```

### Finality Analysis

```{R }
res = getFinality(beliefData,
            alignTimes = TRUE, 
            threshold = 0.9,
            arrivalTimes = getTxArrivalTimes(eventData,txVector), 
            horizon = "10:00.000") 
res %>% select(Transaction, successes, trials, p_val = threstest_p_val, point_estimate,ci_low,ci_high)
```

```{R }
ggplot(res, aes(x = Transaction, y = point_estimate)) +
  geom_point(color = "blue") +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.5, color = "lightblue") +
  labs(x = "Transaction", 
       y = "Estimated probability of success",
       title = "Point estimates with 95% CI") +
  theme_minimal()
```

```{R }
getTimeToFinality(test.plain.data, 0.9)
```

### Transaction History

```{R eval = FALSE, echo = FALSE}
getTransactionHistory(eventData,blockData,txVector = c(5), simVector = c(10,10))
```

# Catch-up Attack Cases

## Overview

-   **Configuration:** `examples/configs/test/XXX`
-   **Workload Sampler:** `examples/configs/test/XXXX.csv`
-   **Runs With:** \``test-XXXX.sh`

## Attack - Caching up: -1,0,10%

```{r}
#experiment = "test.attack.control - 2026.01.31 17.15.52"
experiment = "catchup.attack.-1.0.10 - 2026.02.20 16.36.10"
setVars("../../../../cnsim-bitcoin/examples/results/",experiment, c(50,60,70,80,90))
```

### Pace Analysis

```{R }
paceInfo(outputRelFolder,experiment)
```

### Data Preparation

```{R }
graphData.attack.1.10 = prepareGraphData(beliefData,
                                alignTimes = TRUE,
                                VaR = TRUE,
                                arrivalTimes = getTxArrivalTimes(eventData,txVector))

beliefData.attack.1.10 <- beliefData
```

```{R }
getBeliefGraph(graphData.attack.1.10, xlim = c("0:00","0:15:00"),threshold = 0.9, VaR = "exclude")
```

### Finality Analysis - Theoretical

```{R }
q = 0.1
p = 0.9
z = 1
q_z = (q/p)^z
```

The probability that the attack will ever catch up from $z$ blocks behind given the $q*10$/$p*10$ ratio is $q_z$.

### Finality Analysis - Empirical

```{R }
res.attack.1.10 = getFinality(beliefData.attack.1.10,
            alignTimes = TRUE, 
            threshold = 0.9,
            arrivalTimes = getTxArrivalTimes(eventData,txVector), 
            horizon = "10:00.000") 
```

```{R }
(res.conciseres.attack.1.10 <- res.attack.1.10 %>% mutate(theoretical = (1- q_z)) %>%
  select(Transaction, successes, trials, p_val = threstest_p_val, 
         point_estimate, ci_low, theoretical, ci_high))
```

```{R }
target <- res.conciseres.attack.1.10 %>% filter(Transaction == 70)
equivalence(target$trials, target$successes, target$theoretical, delta = 0.08)
```

```{R }
ggplot(res.conciseres.attack.1.10, aes(x = Transaction, y = point_estimate)) +
  geom_point(color = "blue") +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.5, color = "lightblue") +
  labs(x = "Transaction", 
       y = "Estimated probability of success",
       title = "Point estimates with 95% CI") +
   annotate("text",
           x = Inf,
           y = target$theoretical,
           label = "Theoretical",
           hjust = 1.1,
           vjust = -0.5) + 
  geom_hline(yintercept = target$theoretical,
             linetype = "dashed") +
  theme_minimal()
```

```{R }
getTimeToFinality(graphData.attack.1.10, 0.9)
```

## Attack 5-30%

```{r}
experiment = "catchup.attack.-5.0.30 - 2026.02.20 16.36.13"
setVars("../../../../cnsim-bitcoin/examples/results/",experiment, c(50,60,70,80,90))
```

### Pace Analysis

```{R }
paceInfo(outputRelFolder,experiment)
```

### Data Preparation

```{R }
graphData.attack.5.30 = prepareGraphData(beliefData,
                                alignTimes = TRUE,
                                VaR = TRUE,
                                arrivalTimes = getTxArrivalTimes(eventData,txVector))

beliefData.attack.5.30 <- beliefData
```

```{R }
getBeliefGraph(graphData.attack.5.30, xlim = c("0:00","0:15:00"),threshold = 0.9, VaR = "exclude")
```

### Finality Analysis - Theoretical

```{R }
q = 0.3
p = 0.7
z = 5
(q_z = (q/p)^z)
```

The probability that the attack will ever catch up from $z$ blocks behind given the $q*10$/$p*10$ ratio is $q_z$.

### Finality Analysis - Empirical

```{R }
res.attack.5.30 = getFinality(beliefData.attack.5.30,
            alignTimes = TRUE, 
            threshold = 0.9,
            arrivalTimes = getTxArrivalTimes(eventData,txVector), 
            horizon = "10:00.000") 
```

```{R }
(res.concise.attack.5.30 <- res.attack.5.30 %>% mutate(theoretical = (1- q_z)) %>%
  select(Transaction, successes, trials, p_val = threstest_p_val, 
         point_estimate, ci_low, theoretical, ci_high))
```

```{R }
target <- res.concise.attack.5.30 %>% filter(Transaction == 70)
equivalence(target$trials, target$successes, target$theoretical, delta = 0.08)

```

```{R }
ggplot(res.concise.attack.5.30, aes(x = Transaction, y = point_estimate)) +
  geom_point(color = "blue") +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.5, color = "lightblue") +
  labs(x = "Transaction", 
       y = "Estimated probability of success",
       title = "Point estimates with 95% CI") +
   annotate("text",
           x = Inf,
           y = target$theoretical,
           label = "Theoretical",
           hjust = 1.1,
           vjust = -0.5) + 
  geom_hline(yintercept = target$theoretical,
             linetype = "dashed") +
  theme_minimal()
```

```{R }
getTimeToFinality(graphData.attack.5.30, 0.9)
```

# Confirmation Depth Attack Cases

## Overview

-   **Configuration:** `examples/configs/test/XXX`
-   **Workload Sampler:** `examples/configs/test/XXXX.csv`
-   **Runs With:** \``test-XXXX.sh`

## Attack - Confirmations: Advantage = 0, Confirmations = 1, Share: 10%

```{r}
#experiment = "test.attack.control - 2026.01.31 17.15.52"
experiment = "confirmation.attack.0.1.10 - 2026.02.22 20.25.54"
setVars("../../../../cnsim-bitcoin/examples/results/",experiment, c(50,60,70,80,90))
```

### Pace Analysis

```{R }
paceInfo(outputRelFolder,experiment)
```

### Data Preparation

```{R }
graphData.confirmation.0.1.10 = prepareGraphData(beliefData,
                                alignTimes = TRUE,
                                VaR = TRUE,
                                arrivalTimes = getTxArrivalTimes(eventData,txVector))

beliefData.confirmation.0.1.10 <- beliefData
```

```{R }
getBeliefGraph(graphData.confirmation.0.1.10, xlim = c("0:00","0:45:00"),threshold = 0.9, VaR = "exclude")
```

### Finality Analysis - Theoretical

```{R }
q = 0.1
z = 1
(P = attacker_success_probability(q,z))
# P = 0.20 # From paper!
P = 0.056 # From paper!
```

The probability that the attack will ever catch up after the target block has received $z$ confirmations is $P$.

### Finality Analysis - Empirical

```{R }
res.confirmation.0.1.10 = getFinality(beliefData.confirmation.0.1.10,
            alignTimes = TRUE, 
            threshold = 0.9,
            arrivalTimes = getTxArrivalTimes(eventData,txVector), 
            horizon = "1:40:00.000") 
```

```{R }
(res.conciseres.confirmation.0.1.10 <- res.confirmation.0.1.10 %>% mutate(theoretical = (1- P)) %>%
  select(Transaction, successes, trials, p_val = threstest_p_val, 
         point_estimate, ci_low, theoretical, ci_high))
```

```{R }
target <- res.conciseres.confirmation.0.1.10 %>% filter(Transaction == 70)
equivalence(target$trials, target$successes, target$theoretical, delta = 0.1)
```

```{R }
ggplot(res.conciseres.attack.1.10, aes(x = Transaction, y = point_estimate)) +
  geom_point(color = "blue") +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.5, color = "lightblue") +
  labs(x = "Transaction", 
       y = "Estimated probability of success",
       title = "Point estimates with 95% CI") +
   annotate("text",
           x = Inf,
           y = target$theoretical,
           label = "Theoretical",
           hjust = 1.1,
           vjust = -0.5) + 
  geom_hline(yintercept = target$theoretical,
             linetype = "dashed") +
  theme_minimal()
```

```{R }
getTimeToFinality(graphData.attack.1.10, 0.9)
```

## Attack - Confirmations: Advantage = 0, Confirmations = 5, Share: 30%

```{r}
#experiment = "test.attack.control - 2026.01.31 17.15.52"
experiment = "confirmation.attack.0.5.30 - 2026.02.22 20.46.15"
setVars("../../../../cnsim-bitcoin/examples/results/",experiment, c(50,60,70,80,90))
```

### Pace Analysis

```{R }
paceInfo(outputRelFolder,experiment)
```

### Data Preparation

```{R }
graphData.confirmation.0.5.30 = prepareGraphData(beliefData,
                                alignTimes = TRUE,
                                VaR = TRUE,
                                arrivalTimes = getTxArrivalTimes(eventData,txVector))

beliefData.confirmation.0.5.30 <- beliefData
```

```{R }
getBeliefGraph(graphData.confirmation.0.5.30, xlim = c("0:00","0:45:00"),threshold = 0.9, VaR = "exclude")
```

### Finality Analysis

```{R }
res.confirmation.0.5.30 = getFinality(beliefData.confirmation.0.5.30,
            alignTimes = TRUE, 
            threshold = 0.9,
            arrivalTimes = getTxArrivalTimes(eventData,txVector), 
            horizon = "1:10:00.000") 
```

```{R }
q = 0.3
z = 5
(P = attacker_success_probability(q,z))
P = 0.19762 # From paper!
P = 0.15645 # From paper!
```

The probability that the attack will ever catch up after the target block has received $z$ confirmations is $P$.

```{R }
(res.conciseres.confirmation.0.5.30 <- res.confirmation.0.5.30 %>% mutate(theoretical = (1- P)) %>%
  select(Transaction, successes, trials, p_val = threstest_p_val, 
         point_estimate, ci_low, theoretical, ci_high))
```

```{R }
target <- res.conciseres.confirmation.0.5.30 %>% filter(Transaction == 70)
equivalence(target$trials, target$successes, target$theoretical, delta = 0.1)
```

```{R }
ggplot(res.conciseres.confirmation.0.5.30, aes(x = Transaction, y = point_estimate)) +
  geom_point(color = "blue") +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.5, color = "lightblue") +
  labs(x = "Transaction", 
       y = "Estimated probability of success",
       title = "Point estimates with 95% CI") +
   annotate("text",
           x = Inf,
           y = target$theoretical,
           label = "Theoretical",
           hjust = 1.1,
           vjust = -0.5) + 
  geom_hline(yintercept = target$theoretical,
             linetype = "dashed") +
  theme_minimal()
```

```{R }
getTimeToFinality(graphData.attack.1.10, 0.9)
```

## Attack - Confirmations: Advantage = 0, Confirmations = 6, Share: 40%

```{r}
#experiment = "test.attack.control - 2026.01.31 17.15.52"
experiment = "confirmation.attack.0.6.40 - 2026.02.23 00.09.07"
setVars("../../../../cnsim-bitcoin/examples/results/",experiment, c(50,60,70,80,90))
```

### Pace Analysis

```{R }
paceInfo(outputRelFolder,experiment)
```

### Data Preparation

```{R }
graphData.confirmation.0.6.40 = prepareGraphData(beliefData,
                                alignTimes = TRUE,
                                VaR = TRUE,
                                arrivalTimes = getTxArrivalTimes(eventData,txVector))

beliefData.confirmation.0.6.40 <- beliefData
```

```{R }
getBeliefGraph(graphData.confirmation.0.6.40, xlim = c("0:00","3:45:00"),threshold = 0.9, VaR = "exclude")
```

### Finality Analysis

```{R }
res.confirmation.0.6.40 = getFinality(beliefData.confirmation.0.6.40,
            alignTimes = TRUE, 
            threshold = 0.9,
            arrivalTimes = getTxArrivalTimes(eventData,txVector), 
            horizon = "3:10:00.000") 
```

```{R }
q = 0.4
z = 7
(P = attacker_success_probability(q,z))

P = 0.45769 # From paper!
```

The probability that the attack will ever catch up after the target block has received $z$ confirmations is $P$.

```{R }
(res.conciseres.confirmation.0.6.40 <- res.confirmation.0.6.40 %>% mutate(theoretical = (1- P)) %>%
  select(Transaction, successes, trials, p_val = threstest_p_val, 
         point_estimate, ci_low, theoretical, ci_high))
```

```{R }
target <- res.conciseres.confirmation.0.6.40 %>% filter(Transaction == 70)
equivalence(target$trials, target$successes, target$theoretical, delta = 0.1)
```

```{R }
ggplot(res.conciseres.confirmation.0.6.40, aes(x = Transaction, y = point_estimate)) +
  geom_point(color = "blue") +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.5, color = "lightblue") +
  labs(x = "Transaction", 
       y = "Estimated probability of success",
       title = "Point estimates with 95% CI") +
   annotate("text",
           x = Inf,
           y = target$theoretical,
           label = "Theoretical",
           hjust = 1.1,
           vjust = -0.5) + 
  geom_hline(yintercept = target$theoretical,
             linetype = "dashed") +
  theme_minimal()
```

```{r }

knitr::knit_exit()
```
